ACP Baseline Model Report:\\ {Evaluation of NEWS on the SRFT Dataset}

### 2022-09-26 TeX/baseline/paper.tex
Cleanup

\usepackage[
    backend=biber,
    style=numeric,
    url=false,
    isbn=false,
    doi=false
  ]{biblatex}
\addbibresource{references.bib}

@@

The NEWS was not effective in detecting which patients in our data would be readmitted to the same hospital in the future. Prior work has found that clinical data indicating the severity of the patient's condition, including constructed scores, is useful in predicting 30-day readmission \cite[pp.~5]{Mahmoudim20}. Dedicated systems for predicting 30-day readmission, such as the HOSPITAL and LACE score, use parameters that the NEWS does not, such as blood test results, procedures the patient underwent, comorbidities and LOS \cite{Donze13}.

>>>>

\usepackage[
    backend=biber,
    style=numeric,
    url=false,
    isbn=false,
    doi=false
  ]{biblatex}
\addbibresource{../../literature/references.bib}

@@

The NEWS was not effective in detecting which patients in our data would be readmitted to the same hospital in the future. Prior work has found that clinical data indicating the severity of the patient's condition, including constructed scores, is useful in predicting 30-day readmission \cite[pp.~5]{Mahmoudi20}. Dedicated systems for predicting 30-day readmission, such as the HOSPITAL and LACE score, use parameters that the NEWS does not, such as blood test results, procedures the patient underwent, comorbidities and LOS \cite{Donze13}.
